---
title: "Function work flow example"
author: "Yi-Han Tang"
date: "2021/4/23"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The package will used in this example
```{r}
library(ggplot2)
library(dplyr)
library(yihanfinalproject)
```

Read the data and input it into R. 
```{r}
data<- read.csv(file.choose(),header = TRUE)

data
```

Calculate the two BMI(before & after) of participants by using function cal_bmi() and insert new column for the results
```{r}

data$first_BMI <- cal_bmi(data$height, data$weight.1..Before.)
data$second_BMI <-cal_bmi(data$height, data$weight.2..after.)

data
```

Check the qualify of each participants (the weight should use weight 1). Increase a column to show the results. After that, using filter() to filter the participants who are "Eligile".
```{r}
data$checkstate <- check_check(data$age, data$height, data$weight.1..Before.)

newdata <- filter(data, data$checkstate == "Eligile")

newdata
```


Summay each group(drug frequency) and input extra participants to each group have same participants
```{r}
count(newdata, drug_frequency)
data2 <-read.csv(file.choose(),header = TRUE)
#calculate BMI(before & after)
data2$first_BMI <- cal_bmi(data2$height, data2$weight.1..Before.)
data2$second_BMI <-cal_bmi(data2$height, data2$weight.2..after.)
#check qualify
data2$checkstate <- check_check(data2$age, data2$height, data2$weight.1..Before.)

#combine two dataframe
total <- rbind(newdata, data2)

head(total)

# organize dataframe
arrange(total,drug_frequency)


```

Use total(dataset) to see the different results by different varies.
First, to see the BMI distribution of participants of different ages by using finction plotage(). And using plotage_separate() to see in different drug frequency, the age distribution of participants.
```{r}
Before1 <- plotage(total$age,total$height, total$weight.1..Before., total$drug_frequency)
After1 <- plotage(total$age, total$height, total$weight.2..after.,total$drug_frequency)

Before1
After1

Before_separte1 <- plotage_separate(total, total$age,total$height, total$weight.1..Before., total$drug_frequency)
After_separte1 <- plotage_separate(total, total$age, total$height, total$weight.2..after.,total$drug_frequency)

Before_separte1
After_separte1

```

Using plotgender() and plotgender_separate() to see the different results by gender.
```{r}
genderbefore <-plotgender(total$age, total$height, total$weight.1..Before.)
genderafter <- plotgender(total$age, total$height, total$weight.2..after.)

genderbefore
genderafter
# using plotgender_separate() to separate in different plots

genderbeforese <-plotgender_separate(total, total$age, total$height, total$weight.1..Before., total$gender)
genderafterse <- plotgender_separate(total,total$age, total$height, total$weight.2..after., total$gender )

genderbeforese
genderafterse
```

